Density dependence

### 2020-10-07 R/density dependence.Rmd
finalizing and writing about density dependence

- Get confidence intervals for cross-basis predictions.  Plot slices with confidence bands.

@@

```{r}
g_growth <-
  gam(shts_next ~ 
        # s(ha_id_number, bs = "re") + #this takes waaay too long to converge
        s(plot, bs = "re") +
        log_shts + #when modeled as a spline, edf is essentially a line
        habitat +
        s(Q, L,
          bs = "cb",
          xt = list(bs = "cr")),
      family = gaussian(link = "log"),
      data = ha_sub,
      method = "REML")
```

@@

```{r}
ggplot(pred_growth %>% filter(min_dist < 0.1),
       aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  geom_contour(color = "grey50", size = 0.4) + 
  scale_y_continuous("distance (m)", expand = c(0,0)) +
  scale_x_continuous("conspecific density (shoots/m^2)", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A")
```

@@

```{r}
ggplot(pred_growth %>% filter(lag == 0.75),
       aes(x = x, y = exp(fitted), ymin = exp(fitted - 1.96*se.fit), ymax = exp(fitted + 1.96*se.fit))) +
  geom_line() + 
  geom_ribbon(alpha = 0.3) +
  geom_point(data = ha_sub, aes(x = shts_0.5_1, y = shts_next), inherit.aes = FALSE) +
  coord_cartesian(ylim = c(0,20))
```

- TODO: Try with Florestal (really huge plants there)
- 5750 only: essentially flat surface, except for positive density dependence at 5m.  Seems spurious, would want to see CI.
- CF only: similar.  Essentially flat except for impossibly large positive density dependence at 5 m (expected value of 200+ shoots at highest conspecific density)
- 3-shoot plants only: No significant effect of density.
- Full dataset: Significant, but same pattern.  Large effects only at 5m.  Probably driven by a few extreme values of high-density plots.

>>>>

- Get confidence intervals for cross-basis predictions.  Plot slices with confidence bands.
- Try with just Florestal (really huge plants there)

@@

```{r}
g_growth <-
  gam(shts_next ~ 
        # s(ha_id_number, bs = "re") + #this takes waaay too long to converge
        s(plot, bs = "re") +
        log_shts + #when modeled as a spline, edf is essentially a line
        habitat +
        s(Q, L,
          bs = "cb",
          k = c(2,2),
          xt = list(bs = "cr")),
      family = gaussian(link = "log"),
      data = ha_sub,
      method = "REML")
```

@@

```{r}
pred_growth %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  geom_contour(color = "grey50", size = 0.4) + 
  scale_y_continuous("distance (m)", expand = c(0,0)) +
  scale_x_continuous("conspecific density (shoots/m^2)", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A")
```

@@

```{r}
pred_growth %>%
  filter(min_dist < 0.1) %>% 
  filter(lag == 0.75) %>% 
  ggplot(aes(x = x, y = exp(fitted), ymin = exp(fitted - 1.96*se.fit), ymax = exp(fitted + 1.96*se.fit))) +
  geom_line() + 
  geom_ribbon(alpha = 0.3) +
  geom_point(data = ha_sub, aes(x = shts_0_0.5, y = shts_next), inherit.aes = FALSE) +
  coord_cartesian(ylim = c(0,20))
```

- 5750 only: essentially flat surface, except for positive density dependence at 5m.  Seems spurious, would want to see CI.
- CF only: similar.  Essentially flat except for impossibly large positive density dependence at 5 m (expected value of 200+ shoots at highest conspecific density)
- 3-shoot plants only: No significant effect of density.
- Full dataset: Significant, but same pattern.  Large effects only at 5m.  Probably driven by a few extreme values of high-density plots.
